Models

### 2022-04-20 analysis/05_model_metrics.Rmd
Clarifications

missing_mods <- setdiff(uniq_mods, uniq_metric_model)
```

Write out table of model estimates for manuscript
```{r}
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model, model_id, warning, statistic, df)) %>% 
  write_csv(here::here("figures", "man_model_table.csv"))
```

>>>>

#this is a list of models that weren't fit because there weren't enough timeseries OR they didn't converge
#min_litter_size just won't converge
missing_mods <- setdiff(uniq_mods, uniq_metric_model)
```

Write out table of model estimates for manuscript
```{r}
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model_id, warning, statistic, df)) %>% 
  write_csv(here::here("figures", "man_model_table.csv"))
```
